%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{multicol}
\usepackage[none]{hyphenat}

 
\begin{document}

\header{ewald}{zietsman}{software developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
18 Gordon Rd
Observatory
Cape Town
South Africa
~
082 735 4048
021 448 2040
~
\href{mailto:ewald.zietsman@gmail.com}{ewald.zietsman@gmail.com}
\href{http://za.linkedin.com/in/ewaldzietsman/}{linkedin.com/in/ewaldzietsman}
\section{languages}
english 
afrikaans
\section{personal info}
age: 32
nationality: South African
ID: 8202085009086
\section{programming languages}
python
javascript
\LaTeX
cython
fortran
java
c++
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2009 -- 2011 \\(Incomplete)}
{\textbf PhD Astrophysics and Space Science}
{University of South Africa}
{\emph{Thesis : A Study of Selected Magnetic Cataclysmic Variables}

\emph{Relevant skills:
    \begin{itemize}
        \item Reduction and analysis of high time-resolution observations obtained using the Southern African Large Telescope (SALT)
        \item Computationally intensive calculations (genetic algorithms, utilising neural networks) performed
        using ROCKS cluster computing environment.
        \item Scientific observations using the High-speed polarimeter (HIPPO) on the SAAO 1.9m telescope in
        Sutherland
        \item Development of custom analysis and visualisation software using Python and related tools.
\end{itemize}}
}
%------------------------------------------------
%------------------------------------------------
\entry
{2006 -- 2008}
{\textbf M.Sc. Astrophysics and Space Science}
{University of Cape Town}
{\emph{Coursework: Plasma Physics, Magnetohydrodynamics, Extragalactic Astronomy, Observational
Cosmology, Cataclysmic Variables}

\emph{Dissertation: High-speed Photometry and Spectroscopy of the Cataclysmic Variable EC2117-54 : Exploring New Avenues With the Southern African Large Telescope }}
%------------------------------------------------
\entry
{2005}
{\textbf B.Sc.(Hons) Astrophysics and Space Science}
{University of Cape Town}
{\emph{Coursework: Electrodynamics, Quantum Mechanics, Stellar Atmospheres, Stellar Structure and Evolution, Computational Physics, General Relativity, Galaxies, Observational Techniques, Radio Astronomy}}
%------------------------------------------------
\entry
{2001 -- 2004}
{\textbf B.Sc. Geomatics}
{University of Cape Town}
{\emph{Coursework: Surveying, Geographic Information Systems, Computer Science, Remote Sensing,
Mathematics, Physics, Astronomy, Numerical Methods, Land Law, Engineering Surveying,
Photogrammetry}}
%------------------------------------------------
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2011 --}
{\href{http://www.siyavula.com}{\underline{Siyavula Education}}}
{Cape Town}
{\emph{User experience \& interface designer, project manager, webmaster, quality assurance (QA) tester, copywriter, Mathematical Literacy textbook content coordinator \& author.}}
%------------------------------------------------

\entry
{2010 -- 2011}
{Barrington Studios}
{Cape Town}
{\emph{Co-founder \& co-manager of music studio and live performance venue.}}
%------------------------------------------------



\entry
{}
{Ifo Music}
{Cape Town}
{\emph{Administrator \& project manager.}}
%------------------------------------------------

\entry
{2009 -- 2011}
{Tiny Sunshine Music}
{Cape Town}
{\emph{Co-founder. Artists \& events manager. Virtual assistant \& project administrator.}}
%------------------------------------------------


\entry
{2008 -- 2010}
{St Cyprian's School}
{Cape Town}
{\emph{Part-time cello teacher, Grades R-12.}}
%------------------------------------------------
\entry
{2008 -- 2009}
{\href{http://www.classical.com}{\underline{classical.com}}}
{London/Cape Town}
{\emph{Web content editor \& graphic designer.}}
%------------------------------------------------


\entry
{2008 -- 2011}
{Self-employed}
{Cape Town}
{\emph{Freelance project administrator, web \& graphic designer, virtual assistant, copywriter and musician.}}
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2004 -- 2006}
{University of Cape Town Dean's Merit List}
{Cape Town}
{}
%------------------------------------------------
\entry
{2002 -- 2003}
{University of the Witwatersrand Dean's Merit List}
{Johannesburg}
{}
%------------------------------------------------
\entry
{2002}
{University of the Witwatersrand Council Entrance Scholarship}
{Johannesburg}
{}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
%	PROFESSIONAL QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{professional qualifications}

\begin{entrylist}
%------------------------------------------------
\entry
{2009}
{International Computer Driving License}
{ICDL via UNISA}
{\emph{Microsoft Windows, Microsoft Office, Internet}}

%------------------------------------------------
\entry
{2008}
{Licentiate of the Associated Board of the Royal Schools of Music}
{ABRSM}
{\emph{Performance, cello}}

%------------------------------------------------
\entry
{2003}
{Diploma of the Associated Board of the Royal Schools of Music}
{ABRSM}
{\emph{Performance, cello}}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{skills}

\begin{itemize}
\item User experience and interface design, including responsive/mobile design.
\item Prototyping, usability testing, heuristic evaluation.
\item Project management and administration.
\item Quality assurance testing.
\item Graphic and website design, webmastering, desktop publishing, research.
\item English and Mathematics authoring, editing, proof-reading and copywriting.

\end{itemize}

\textbf{Operating systems}
\begin{multicols}{2}
\begin{itemize}
 \item Microsoft Windows
 \item Ubuntu
 \item iOS7
 \item Android
\end{itemize}
\end{multicols}

\textbf{Software}
\begin{multicols}{2}
\begin{itemize}
 \item GitHub
 \item LaTeX
 \item GVim
 \item Jekyll
  \item Adobe Photoshop
 \item Balsamiq
 \item Inkscape
 \item GIMP
 \item PSTricks
 \item TikZ
 \item Google Drive
 \item Microsoft Office
\end{itemize}
\end{multicols}

\textbf{Markup and programming languages}\\
\\
Comprehensive knowledge of: 
\begin{itemize}
 \item HTML5
 \item CSS3
 \item XML
 \item CNXML+
 \item MathML
 \end{itemize}
Working knowledge of Javascript, JQuery, Python, C++, Java.

\textbf{Other}
\begin{itemize}
\item Knowledge of and experience with Bootstrap, Wordpress, Plone, EPUB3.0 and Google Analytics.
 \item Familiarity with social media and digital marketing tools including Facebook, Twitter, LinkedIn and Tumblr.
 \item Fluency in English and conversational Afrikaans, working knowledge of French.
 \item Driver's license (code B) and own car.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PORTFOLIO SECTION
%----------------------------------------------------------------------------------------

\section{portfolio}
\begin{sitelist}

%------------------------------------------------
\site
{}
{Siyavula Education: \href{http://www.siyavula.com}{\underline{www.siyavula.com}}}
{}
{\emph{Project management, project specification, UX, collaborative graphic design, copywriting, testing.}}

%------------------------------------------------

\site
{}
{The Thunderbolt Kids: \href{http://thunderboltkids.co.za}{\underline{thunderboltkids.co.za}}}
{}
{\emph{Project management, project specification, research, site structure, UX, testing.}}

%------------------------------------------------
\site
{}
{Everything Maths: \href{http://www.everythingmaths.co.za}{\underline{everythingmaths.co.za}}}
{}
{\emph{UX, project specification, graphic design, copywriting, testing.}}

%------------------------------------------------


\site
{}
{Nicola du Toit: \href{http://www.nicoladutoit.com/ux-portfolio}{\underline{nicoladutoit.com}}}
{}
{\emph{Jekyll and Lightbox2 implementation, customised CSS (including Bootstrap), copywriting, proofreading, testing.}}
%------------------------------------------------
\end{sitelist}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\section{publications}
\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{Designing an interface to provide new
functionality for the post-processing of
web-based annotations}
{University of Cape Town}
{\emph{
Dissertation submitted in partial fulfilment of the requirements
for the degree of Master of Philosophy in Information Technology.} 
 }



%------------------------------------------------
\entry
{2013}
{Everything Maths Literacy Grade 10}
{Siyavula Education}
{\emph{Project management, textbook content coordination, authoring, editing, graphic design, proofreading.}}
%------------------------------------------------

\entry
{2012}
{Everything Maths Grade 10}
{Siyavula Education}
{\emph{Technical editing, textbook authoring, graphic design, proofreading.}}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{Professional:} human-computer interaction, usability, cognitive psychology, visual design.

\textbf{Personal:} music, science, photography, dragon boating, trail running, flyball (dog agility).

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------

\section{references}

Dr Mark Horner\\
Siyavula Education\\
mark@siyavula.com\\
\\
Dr Carl Scheffler\\
Siyavula Education\\
carl@siyavula.com\\

\end{document}
